Delivering Reliable Software in the European Scientific Arena: Evolution of Methodologies and New Trend Analysis

### 2017-12-19 paper-ieee-trans.tex
fixed fig issue

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{images/confman.png}
\caption{Trend line showing the adoption of Configuration Management tools throughout the project lifetime.}
\label{fig:fig_confman}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{images/pilotpreview.png}
\caption{Resource centers supporting the Pilot Preview testbed and corresponding
set of deployed INDIGO-DataCloud components or services.}
\label{fig:fig_confman}
\end{figure*}

@@

\begin{IEEEbiography}{Mario David}
Biography text here.
\end{IEEEbiography}

@@

\begin{IEEEbiography}{J. Gomes}
Biography text here.
\end{IEEEbiography}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth, height=50mm]{images/confman.png}
\caption{Trend line showing the adoption of Configuration Management tools throughout the project lifetime.}
\label{fig:fig_confman}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{images/pilotpreview.png}
\caption{Resource centers supporting the Pilot Preview testbed and corresponding
set of deployed INDIGO-DataCloud components or services.}
\label{fig:fig_pilotpreview}
\end{figure*}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/mario-david}}]{Mario David}
Mario David is a research associate at LIP. He holds a PhD in Experimental Particle Physics from the University of Lisbon.
Member of DEEP-HybridDatacloud project as Work Package leader of Testbed and integration with EOSC services. Member of EOSC-Hub project and
of the Portuguese National Computing Distributed Infrastructure.
He held a research associate position at Institut de Physique du Globe de Paris (IPGP/CNRS) as Scientific Software Developer for the VERCE project, in particular in the data intensive use cases for seismology.
He was been actively involved in the Validation, Quality Assurance and testing of middleware, in regional and global operations.
\end{IEEEbiography}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/jorge-gomes}}]{Jorge Gomes}
Jorge Gomes is a computing researcher at LIP. He worked in the development of advanced data acquisition systems at CERN, and participated in pioneering projects in the domain of digital satellite data communications, IP over ATM, and advanced videoconferencing over IP networks. Since 2001 he has participated in numerous projects regarding distributed computing, networks and security in Europe and Latin America. He is the head of the LIP Advanced Computing and Digital Infrastructures Group and technical coordinator of the Portuguese National Grid Infrastructure, representative of Portugal in the Council of the European Grid Infrastructure (EGI) and responsible for the Portuguese participation in IBERGRID, that joins Portuguese and Spanish distributed computing infrastructures.
\end{IEEEbiography}
